Slovene NLTK Tagger

### 2012-01-15 paper/paper.tex
Added Brill algorithm.

\subsection{Naive Bayes classifier}
Both Brill and Trigram are sequential backoff taggers. Meanwhile, Naive Bayes is a \textit{classifier based tagger}.
Classification is a process where, for a given output, we have to choose the correct class. Basically, it is  procedure for assigning input data into one of a given categories.

@@

\begin{thebibliography}{99}
\bibitem{nltk} (2011) NLTK web page. [Online]. Available at: \url{http://www.nltk.org/}
\bibitem{JOS} (2011) JOS project web page. [Online]. Available at: \url{http://nl.ijs.si/jos/}
\bibitem{nltk-trainer} (2011) NLTK-trainer project source code. [Online]. Available at: \url{https://github.com/japerk/nltk-trainer}
\bibitem{MULTEXT-East} (2011) Slovene MULTEXT-East Morphosyntactic Specifications. [Online]. Available at: \url{http://nl.ijs.si/ME/V4/msd/html/msd-sl.html}
\bibitem{NLTKBOOK} S. Bird, E. Klein, and E. Loper. (2009, June). Natural Language Processing with Python \textit{--- Analyzing Text with the Natural Language Toolkit}. (1st ed.) [Online]. Available at: \url{http://www.nltk.org/book}
\bibitem{xml_tags} T. Erjavec. (2011, January 29). TEI Schema for SSJ and JOS corpora of Slovene. [Online].
Available at: \url{http://nl.ijs.si/ssj/schema/tei_ssj_doc.pdf}
\bibitem{tokenizer} (2011) Tokenizers. [Online]. Available at: \url{http://docs.huihoo.com/nltk/0.9.5/guides/tokenize.html}
\bibitem{CODE} (2011) Slovene NLTK Tagger (the source code from our project). [Online]. Available at: \url{https://github.com/nikicc/slovene-nltk-tagger}
\bibitem{wiki} (2011) Wikipedia. [Online]. Available at: \url{http://en.wikipedia.org/wiki/Part-of-speech_tagging}
\end{thebibliography}
\end{document}

>>>>

The algorithm starts with the assignment of tags in a maximum likelihood manner; then improving "patches" are determined via the generation of rules that correct tagging errors made in the initialization phase \cite{brill}:
\begin{itemize}
\item[•]Initialization:
\begin{itemize}
\item[•]Known words (in vocabulary): assigning the most frequent tag associated to a form of the word
\item[•]Unknown words (out of vocabulary) :
\begin{itemize}
\item[•] Proper noun if capitalized and simple noun else
\item[•] Learning or guessing rules with lexical rules on the same basis as contextual rules
\end{itemize}
\end{itemize}

\item[•] Learning Phase:
\begin{itemize}
\item[•] Iteratively compute the error score of each candidate rule (difference between the number of errors before and after applying the rule)
\item[•] Select the best (higher score) rule.
\item[•] Add it to the rule set and apply it to the text.
\item[•] Repeat until no rule has a score above a given threshold (that is, if the chosen threshold is zero (which can lead to over-fitting), until applying new rules leaves the text in the same state, which is then supposed to be the final state of the tagging).
\end{itemize}
\end{itemize}

Lexical rules are used for the initialization, and contextual rules are used to correct the tags.
\begin{itemize}
\item[•] Lexical rules: word to tag IF Condition (example: identification of suffixes like "-tion")
\item[•] Contextual rules: tag1 to tag2 IF Condition (example: "preceding/following tag is X", "preceding/following word is w")       
\end{itemize}
\subsection{Naive Bayes classifier}
Both Brill and Trigram are sequential backoff taggers. Meanwhile, Naive Bayes is a \textit{classifier based tagger}.
Classification is a process where, for a given output, we have to choose the correct class. Basically, it is  procedure for assigning input data into one of a given categories.

@@

\begin{thebibliography}{99}
\bibitem{nltk} (2011) NLTK web page. [Online]. Available at: \url{http://www.nltk.org/}
\bibitem{JOS} (2011) JOS project web page. [Online]. Available at: \url{http://nl.ijs.si/jos/}
\bibitem{nltk-trainer} (2011) NLTK-trainer project source code. [Online]. Available at: \url{https://github.com/japerk/nltk-trainer}
\bibitem{MULTEXT-East} (2011) Slovene MULTEXT-East Morphosyntactic Specifications. [Online]. Available at: \url{http://nl.ijs.si/ME/V4/msd/html/msd-sl.html}
\bibitem{NLTKBOOK} S. Bird, E. Klein, and E. Loper. (2009, June). Natural Language Processing with Python \textit{--- Analyzing Text with the Natural Language Toolkit}. (1st ed.) [Online]. Available at: \url{http://www.nltk.org/book}
\bibitem{xml_tags} T. Erjavec. (2011, January 29). TEI Schema for SSJ and JOS corpora of Slovene. [Online].
Available at: \url{http://nl.ijs.si/ssj/schema/tei_ssj_doc.pdf}
\bibitem{tokenizer} (2011) Tokenizers. [Online]. Available at: \url{http://docs.huihoo.com/nltk/0.9.5/guides/tokenize.html}
\bibitem{CODE} (2011) Slovene NLTK Tagger (the source code from our project). [Online]. Available at: \url{https://github.com/nikicc/slovene-nltk-tagger}
\bibitem{wiki} (2011) Wikipedia. [Online]. Available at: \url{http://en.wikipedia.org/wiki/Part-of-speech_tagging}
\bibitem{brill} (2011) Brill tagger algorithm. [Online]. Available at: \url{http://en.wikipedia.org/wiki/Brill_tagger}
\end{thebibliography}
\end{document}
